---
title: "Exploratory Data Analysis"
format: html
editor: visual
---

```{r}
#| echo: false
#| output: false
library(tidyverse)
library(patchwork)
library(cowplot)
```

```{r}
#| echo: false
#| output: false
data <- read_csv("/Volumes/Thesis/Epstein_Files/output/doc_type_combined.csv")
data_e <- read_csv("/Volumes/Thesis/Epstein_Files/output/email_text_clean.csv")
data_f <- read_csv("/Volumes/Thesis/Epstein_Files/output/extraction_combined.csv")
```

## Total number of files

```{r}
nrow(data)
```

## Total number of pages

```{r}
sum(data$file_length, na.rm = TRUE)
```

```{r}
#| echo: false
data <- data |>
  mutate(
    file_type = fct_relevel(file_type,
                            "audio",
                            "corrupt",
                            "email",
                            "other",
                            "photo",
                            "video")
  )
```

## Total number of files by type

```{r}
#| echo: false
files_by_type <- ggplot(data = data,
       aes(
         x = file_type,
         fill = file_type
       )) +
  scale_fill_manual(values = c(
    audio = "#F35E5A",
    corrupt = "#A89005",
    email = "#17B12B",
    other = "#17B3B7",
    photo = "#5086FF",
    video = "#EF43DC"),
    drop = FALSE
  ) +
  geom_bar() +
  geom_text(aes(label = after_stat(count)), 
            stat = "count",
            size = 6,
            size.unit = "pt",
            vjust = -0.3) +
  scale_y_sqrt() +
  theme_void() +
  theme(
    plot.margin = margin(r = 10, l = 10, b = 10),
    axis.title.y = element_blank(), # remove label
    axis.text.y = element_blank(), # remove number
    axis.ticks.y = element_blank(), # remove ticks
    axis.line.y = element_blank(), # remove line (blank here)
    axis.text.x = element_text(), # restore x tick labels
    axis.title.x = element_blank(), # restore x axis title
    legend.position = "none",
    plot.background = element_rect(fill = "white", color = NA)
        ) + 
  labs(title = "Total number of files by type")
files_by_type
```

## Total number of types by dataset

### Data

```{r}
#| echo: false
data_court <- data |>
  filter(grepl("court-records-", file_origin)) |>
  mutate(file_origin = factor(
    file_origin,
    levels = str_sort(unique(file_origin), numeric = TRUE)
  )) |>
  mutate(file_origin = factor(
    file_origin,
    levels = c(
      'court-records-doe-v-indyke-no-119-cv-08673-sdny-2019',
      'court-records-doe-v-indyke-no-119-cv-11869-sdny-2019',
      'court-records-doe-v-indyke-no-120-cv-00484-sdny-2020',
      'court-records-doe-v-indyke-no-120-cv-02365-sdny-2020',
      'court-records-doe-17-v-indyke-no-119-cv-09610-sdny-2019',
      'court-records-doe-1000-v-indyke-no-119-cv-10577-sdny-2019',
      'court-records-v-indyke-no-119-cv-10474-sdny-2019',
      'court-records-v-indyke-no-119-cv-10475-sdny-2019',
      'court-records-v-indyke-no-119-cv-10476-sdny-2019',
      'court-records-v-indyke-no-119-cv-10479-sdny-2019',
      'court-records-v-indyke-no-119-cv-10788-sdny-2019',
      'court-records-doe-v-united-states-no-908-cv-80736-sd-fla-2008',
      'court-records-united-states-v-noel-no-119-cr-00830-sdny-2019',
      'court-records-united-states-v-maxwell-no-20-3061-2d-cir-2020',
      'court-records-united-states-v-maxwell-no-21-0058-2d-cir-2021',
      'court-records-united-states-v-maxwell-no-21-0770-2d-cir-2021',
      'court-records-united-states-v-maxwell-no-22-1426-2d-cir-2022',
      'court-records-united-states-v-maxwell-no-120-cr-00330-sdny-2020',
      'court-records-united-states-v-maxwell-no-120-mj-00132-dnh-2020',
      'court-records-v-maxwell-no-115-cv-07433-sdny-2015',
      'court-records-v-maxwell-no-117-mc-00025-sdny-2016',
      'court-records-maxwell-v-united-states-no-24-1073-us-2025-petition-cert',
      'court-records-v-nine-east-71st-street-no-119-cv-07625-sdny-2019',
      'court-records-ca-florida-holdings-llc-publisher-palm-beach-post-v-aronberg-no-50-2019-ca-014681-xxxx-mb',
      'court-records-government-united-states-virgin-islands-v-jpmorgan-chase-bank-na-no-122-cv-10904-sdny-2022',
      'court-records-operating-engineers-construction-industry-and-miscellaneous-pension-fund-v-dimon-no-123-cv-03903',
      'court-records-re-grand-jury-05-02-wpb-07-103-wpb-no-925-mc-80920-sd-fla-2025',
      'court-records-doe-no-3-v-epstein-no-908-cv-80232-sd-fla-2008',
      'court-records-doe-no-4-v-epstein-no-908-cv-80380-sd-fla-2008',
      'court-records-doe-no-5-v-epstein-no-908-cv-80381-sd-fla-2008',
      'court-records-doe-no-6-v-epstein-no-908-cv-80994-sd-fla-2008',
      'court-records-doe-no-8-v-epstein-no-909-cv-80802-sd-fla-2009',
      'court-records-jane-doe-43-v-epstein-no-117-cv-00616-sdny-2017',
      'court-records-doe-no-101-v-epstein-no-909-cv-80591-sd-fla-2009',
      'court-records-doe-no-102-v-epstein-no-909-cv-80656-sd-fla-2009',
      'court-records-doe-no-103-v-epstein-no-910-cv-80309-sd-fla-2010',
      'court-records-doe-v-epstein-no-908-cv-80069-sd-fla-2008',
      'court-records-doe-v-epstein-no-908-cv-80119-sd-fla-2008',
      'court-records-doe-v-epstein-no-908-cv-80804-sd-fla-2008',
      'court-records-doe-v-epstein-no-909-v-80469-sd-fla-2009',
      'court-records-v-epstein-909-cv-81092-sd-fla-2009',
      'court-records-v-epstein-no-910-cv-80447-sd-fla-2010',
      'court-records-v-epstein-no-910-cv-81111-sd-fla-2010',
      'court-records-united-states-v-epstein-no-19-2221-2d-cir-2019',
      'court-records-united-states-v-epstein-no-119-cr-00490-sdny-2019',
      'court-records-state-florida-v-epstein-no-50-2006-cf-009454-axxx-mb-fla-15th-cir-ct-2006',
      'court-records-state-florida-v-epstein-no-50-2008-cf-009381-axxx-mb-fla-15th-cir-ct-2008',
      'court-records-epstein-v-no-sc15-2286-fla-sup-ct-2015',
      'court-records-epstein-v-rothstein-no-50-2009-ca-040800-xxxx-mb-fla-15th-cir-ct-2009',
      'court-records-matter-estate-jeffrey-e-epstein-deceased-no-st-21-rv-00005-vi-super-ct-2021',
      'court-records-maxwell-v-estate-jeffrey-epstein-no-st-20-cv-155-vi-super-ct-2020'
    )
  )) |>
  mutate(file_type = factor(file_type, levels = c("audio", "corrupt", "email", "other", "photo", "video")))

court_case_labels <- c(
  'court-records-ca-florida-holdings-llc-publisher-palm-beach-post-v-aronberg-no-50-2019-ca-014681-xxxx-mb' = "CA Florida Holdings v. Aronberg",
  'court-records-doe-v-united-states-no-908-cv-80736-sd-fla-2008' = "Doe v. US",
  'court-records-government-united-states-virgin-islands-v-jpmorgan-chase-bank-na-no-122-cv-10904-sdny-2022' = "US Virgin Islands v. JP Morgan Chase Bank",
  'court-records-operating-engineers-construction-industry-and-miscellaneous-pension-fund-v-dimon-no-123-cv-03903' = "Pension Fund v. Dimon",
  'court-records-re-grand-jury-05-02-wpb-07-103-wpb-no-925-mc-80920-sd-fla-2025' = "In re: Grand Jury 05-02 (WPB)",
  'court-records-united-states-v-maxwell-no-20-3061-2d-cir-2020' = "US v. Maxwell, 3061",
  'court-records-united-states-v-maxwell-no-21-0058-2d-cir-2021' = "US v. Maxwell, 0058",
  'court-records-united-states-v-maxwell-no-21-0770-2d-cir-2021' = "US v. Maxwell, 0770",
  'court-records-united-states-v-maxwell-no-22-1426-2d-cir-2022' = "US v. Maxwell, 1426",
  'court-records-united-states-v-maxwell-no-120-cr-00330-sdny-2020' = "US v. Maxwell, 00330",
  'court-records-maxwell-v-united-states-no-24-1073-us-2025-petition-cert' = "Maxwell v. US",
  'court-records-united-states-v-maxwell-no-120-mj-00132-dnh-2020' = "US v. Maxwell, 00132",
  'court-records-v-maxwell-no-115-cv-07433-sdny-2015' = "[Redacted] v. Maxwell, 07433",
  'court-records-v-maxwell-no-117-mc-00025-sdny-2016' = "[Redacted] v. Maxwell, 00025",
  'court-records-united-states-v-noel-no-119-cr-00830-sdny-2019' = "US v. Noel, 00830",
  'court-records-v-indyke-no-119-cv-10474-sdny-2019' = "[Redacted] v. Indyke, 10474",
  'court-records-v-indyke-no-119-cv-10475-sdny-2019' = "[Redacted] v. Indyke, 10475",
  'court-records-v-indyke-no-119-cv-10476-sdny-2019' = "[Redacted] v. Indyke, 10476",
  'court-records-v-indyke-no-119-cv-10479-sdny-2019' = "[Redacted] v. Indyke, 10479",
  'court-records-v-indyke-no-119-cv-10788-sdny-2019' = "[Redacted] v. Indyke, 10488",
  'court-records-doe-17-v-indyke-no-119-cv-09610-sdny-2019' = "Doe 17 v. Indyke",
  'court-records-doe-1000-v-indyke-no-119-cv-10577-sdny-2019' = "Doe 1000 v. Indyke",
  'court-records-doe-v-indyke-no-119-cv-08673-sdny-2019' = "Doe v. Indyke, 08673",
  'court-records-doe-v-indyke-no-119-cv-11869-sdny-2019' = "Doe v. Indyke, 11869",
  'court-records-doe-v-indyke-no-120-cv-00484-sdny-2020' = "Doe v. Indyke, 00484",
  'court-records-doe-v-indyke-no-120-cv-02365-sdny-2020' = "Doe v. Indyke, 02365",
  'court-records-v-nine-east-71st-street-no-119-cv-07625-sdny-2019' = "[Redacted] v. Nine East 71st St",
  'court-records-doe-no-3-v-epstein-no-908-cv-80232-sd-fla-2008' = "Doe 3 v. Epstein",
  'court-records-doe-no-4-v-epstein-no-908-cv-80380-sd-fla-2008' = "Doe 4 v. Epstein",
  'court-records-doe-no-5-v-epstein-no-908-cv-80381-sd-fla-2008' = "Doe 5 v. Epstein",
  'court-records-doe-no-6-v-epstein-no-908-cv-80994-sd-fla-2008' = "Doe 6 v. Epstein",
  'court-records-doe-no-8-v-epstein-no-909-cv-80802-sd-fla-2009' = "Doe 8 v. Epstein",
  'court-records-doe-no-101-v-epstein-no-909-cv-80591-sd-fla-2009' = "Doe 101 v. Epstein",
  'court-records-doe-no-102-v-epstein-no-909-cv-80656-sd-fla-2009' = "Doe 102 v. Epstein",
  'court-records-doe-no-103-v-epstein-no-910-cv-80309-sd-fla-2010' = "Doe 103 v. Epstein",
  'court-records-doe-v-epstein-no-908-cv-80069-sd-fla-2008' = "Doe v. Epstein, 80069",
  'court-records-doe-v-epstein-no-908-cv-80119-sd-fla-2008' = "Doe v. Epstein, 80119",
  'court-records-doe-v-epstein-no-908-cv-80804-sd-fla-2008' = "Doe v. Epstein, 80804",
  'court-records-doe-v-epstein-no-909-v-80469-sd-fla-2009' = "Doe v. Epstein, 80469",
  'court-records-epstein-v-no-sc15-2286-fla-sup-ct-2015' = "Epstein v. [Redacted]",
  'court-records-epstein-v-rothstein-no-50-2009-ca-040800-xxxx-mb-fla-15th-cir-ct-2009' = "Epstein v. Rothstein",
  'court-records-jane-doe-43-v-epstein-no-117-cv-00616-sdny-2017' = "Doe 43 v. Epstein",
  'court-records-matter-estate-jeffrey-e-epstein-deceased-no-st-21-rv-00005-vi-super-ct-2021' = "Matter of the Estate of Jeffery Epstein",
  'court-records-maxwell-v-estate-jeffrey-epstein-no-st-20-cv-155-vi-super-ct-2020' = "Maxwell v. Estate Jeffery Epstein",
  'court-records-state-florida-v-epstein-no-50-2006-cf-009454-axxx-mb-fla-15th-cir-ct-2006' = "Florida v. Epstein, 009454",
  'court-records-state-florida-v-epstein-no-50-2008-cf-009381-axxx-mb-fla-15th-cir-ct-2008' = "Florida v. Epstein, 009381",
  'court-records-united-states-v-epstein-no-19-2221-2d-cir-2019' = "US v. Epstein, 2221",
  'court-records-united-states-v-epstein-no-119-cr-00490-sdny-2019' = "US v. Epstein, 00490",
  'court-records-v-epstein-909-cv-81092-sd-fla-2009' = "[Redacted] v. Epstein, 81092",
  'court-records-v-epstein-no-910-cv-80447-sd-fla-2010' = "[Redacted] v. Epstein, 80447",
  'court-records-v-epstein-no-910-cv-81111-sd-fla-2010' = "[Redacted] v. Epstein, 81111"
)

data_other <- data |>
  filter(!grepl("court-records-", file_origin)) |>
  filter(!grepl("IMAGES", file_origin)) |>
  filter(!grepl("NATIVE", file_origin)) |>
  filter(!grepl("data-set", file_origin)) |>
  mutate(file_origin = factor(
    file_origin,
    levels = str_sort(unique(file_origin), numeric = TRUE)
  )) |>
  mutate(file_type = factor(file_type, levels = c("audio", "corrupt", "email", "other", "photo", "video")))

others_labels <- c(
    'bop-video-footage' = "Federal Bureau of Prisons Footage",
    'first-phase-declassified-epstein-files' = "First Phase Declassified Files",
    'foia-customs-and-border-protection-cbp' = "Customs and Border Protection",
    'foia-federal-bureau-investigation-fbi' = "Federal Bureau of Investigation",
    'foia-federal-bureau-prisons-bop' = "Federal Bureau of Prisons",
    'foia-florida' = "Florida",
    'maxwell-proffer' = "Prior Disclosure - Maxwell Proffer",
    'memoranda-and-correspondence' = "Prior Disclosure - Memoranda and Corres."
  )

data_sets <- data |>
  filter(grepl("data-set", file_origin)) |>
  mutate(file_origin = factor(
    file_origin,
    levels = str_sort(unique(file_origin), numeric = TRUE)
  )) |>
  mutate(file_type = factor(file_type, levels = c("audio", "corrupt", "email", "other", "photo", "video")))

data_sets_labels <- c(
    'data-set-1-files' = "Dataset 1",
    'data-set-2-files' = "Dataset 2",
    'data-set-3-files' = "Dataset 3",
    'data-set-4-files' = "Dataset 4",
    'data-set-5-files' = "Dataset 5",
    'data-set-6-files' = "Dataset 6",
    'data-set-7-files' = "Dataset 7",
    'data-set-8-files' = "Dataset 8",
    'data-set-9-files' = "Dataset 9",
    'data-set-10-files' = "Dataset 10",
    'data-set-11-files' = "Dataset 11",
    'data-set-12-files' = "Dataset 12"
    )

data_oversight <- data |>
  filter(grepl("IMAGES|NATIVE", file_origin)) |>
  mutate(file_origin = factor(
    file_origin,
    levels = str_sort(unique(file_origin), numeric = TRUE)
  )) |>
  mutate(file_type = factor(file_type, levels = c("audio", "corrupt", "email", "other", "photo", "video")))
```

### Plots

```{r}
totals_court <- ggplot(data_court) +
  aes(file_origin) +
  geom_bar(fill = "grey80", color = "grey78") +
  geom_text(aes(label = after_stat(count)), 
            stat = "count",
            size = 6,
            size.unit = "pt",
            vjust = -0.3) +
  scale_x_discrete(labels = court_case_labels) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,3500)) +
  theme_void() +
  theme(axis.title.y = element_blank(), # remove label
        axis.text.y = element_blank(), # remove number
        axis.ticks.y = element_blank(), # remove ticks
        axis.line.y = element_blank(), # remove line (blank here)
        axis.title.x = element_blank(),
        axis.text.x = element_text(
          size = 6,
          angle = -90,
          hjust = 0,
          vjust = 0.5),
        plot.margin = margin(r = 10, l = 10, b = 10),
        plot.background = element_rect(fill = "white", color = NA)
  ) + 
  labs(title = "Court Cases")

totals_other <- ggplot(data_other) +
  aes(file_origin) +
  geom_bar(fill = "grey80", color = "grey78") +
  geom_text(aes(label = after_stat(count)), 
            stat = "count",
            size = 6,
            size.unit = "pt",
            vjust = -0.3) +
  scale_x_discrete(labels = others_labels) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,3500)) +
  theme_void() +
  theme(axis.title.y = element_blank(), # remove label
        axis.text.y = element_blank(), # remove number
        axis.ticks.y = element_blank(), # remove ticks
        axis.line.y = element_blank(), # remove line (blank here)
        axis.title.x = element_blank(),
        axis.text.x = element_text(
          size = 6,
          angle = -90,
          hjust = 0,
          vjust = 0.5),
        plot.margin = margin(r = 10, l = 10, b = 10),
        plot.background = element_rect(fill = "white", color = NA)
  ) + 
  labs(title = "Other File Origins")

totals_set <- ggplot(data_sets) +
  aes(file_origin) +
  geom_bar(fill = "grey80", color = "grey78") +
  geom_text(aes(label = after_stat(count)), 
            stat = "count",
            size = 6,
            size.unit = "pt",
            vjust = -0.3) +
  scale_x_discrete(labels = data_sets_labels) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) +
  theme_void() +
  theme(axis.title.y = element_blank(), # remove label
        axis.text.y = element_blank(), # remove number
        axis.ticks.y = element_blank(), # remove ticks
        axis.line.y = element_blank(), # remove line (blank here)
        axis.title.x = element_blank(),
        axis.text.x = element_text(
          size = 6,
          angle = -90,
          hjust = 0,
          vjust = 0.5),
        plot.margin = margin(r = 10, l = 10, b = 10),
        plot.background = element_rect(fill = "white", color = NA)
  ) + 
  labs(title = "DOJ Datasets")

totals_oversight <- ggplot(data_oversight) +
  aes(file_origin) +
  geom_bar(fill = "grey80", color = "grey78") +
  geom_text(aes(label = after_stat(count)), 
            stat = "count",
            size = 6,
            size.unit = "pt",
            vjust = -0.3) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,3500)) +
  theme_void() +
  theme(axis.title.y = element_blank(), # remove label
        axis.text.y = element_blank(), # remove number
        axis.ticks.y = element_blank(), # remove ticks
        axis.line.y = element_blank(), # remove line (blank here)
        axis.title.x = element_blank(),
        axis.text.x = element_text(
          size = 6,
          angle = -90,
          hjust = 0,
          vjust = 0.5),
        plot.margin = margin(r = 10, l = 10, b = 10),
        plot.background = element_rect(fill = "white", color = NA)
  ) + 
  labs(title = "Oversight Committee Files")
```

### Plots Combined

```{r}
#| echo: false
top <- totals_oversight | totals_other

combined <- top / totals_court
combined <- combined + plot_layout(heights = c(1,1))
totals_set
```

### Percentage of File Types by Dataset

```{r}
#| echo: false
files_court <- data_court |>
  mutate(court_label = coalesce(court_case_labels[file_origin], file_origin)) |>
  ggplot(aes(x = file_origin, fill = file_type)) +
  geom_bar(position = "fill", width = 0.7) +
  geom_text(
    aes(x = file_origin, y = 0, label = court_label),
    size = 2.5,
    angle = -90,
    hjust = 0,
    nudge_y = -0.05
  ) +
  theme_void() +
  coord_cartesian(clip = "off") +
  theme(
    plot.margin = margin(r = 10, l = 10, b = 10),
    legend.key = element_rect(fill = NA, color = NA),
    legend.text = element_text(size = 9),
    legend.title = element_text(size = 10, face = "bold"),
    legend.position = "none",
    plot.background = element_rect(fill = "white", color = NA)
  ) +
  scale_y_continuous(limits = c(-1, 1)) +
  labs(title = "Court Cases")

files_other <- data_other |>
  mutate(other_label = coalesce(others_labels[file_origin], file_origin)) |>
  ggplot(aes(x = file_origin, fill = file_type)) +
  geom_bar(position = "fill", width = 0.7) +
  geom_text(
    aes(x = file_origin, y = 0, label = other_label),
    size = 2.5,
    angle = -90,
    hjust = 0,
    nudge_y = -0.05
  ) +
  theme_void() +
  coord_cartesian(clip = "off") +
  theme(
    plot.margin = margin(r = 10, l = 10, b = 10),
    legend.key = element_rect(fill = NA, color = NA),
    legend.text = element_text(size = 9),
    legend.title = element_text(size = 10, face = "bold"),
    legend.position = "none",
    plot.background = element_rect(fill = "white", color = NA)
  ) +
  scale_y_continuous(limits = c(-1, 1)) +
  labs(title = "Other File Origins",
       fill = "File Type")

files_oversight <- ggplot(data_oversight) +
  aes(x = file_origin, fill = file_type) +
  geom_bar(position = "fill", width = 0.7) +
  geom_text(
    aes(x = file_origin, y = 0, label = file_origin),
    size = 2.5,
    angle = -90,
    hjust = 0,
    nudge_y = -0.05
  ) +
  scale_y_continuous(limits = c(-1, 1)) +
  theme_void() +
  coord_cartesian(clip = "off") +
  theme(
    plot.margin = margin(r = 10, l = 10, b = 10),
    legend.key = element_rect(fill = NA, color = NA),
    legend.text = element_text(size = 9),
    legend.title = element_text(size = 10, face = "bold"),
    legend.position = "none",
    plot.background = element_rect(fill = "white", color = NA)
  ) +
  labs(title = "Oversight Committee Files")

files_sets <- data_sets |>
  mutate(data_set_label = coalesce(data_sets_labels[file_origin], file_origin)) |>
  ggplot(aes(x = file_origin, fill = file_type)) +
  geom_bar(position = "fill", width = 0.7) +
  geom_text(
    aes(x = file_origin, y = 0, label = data_set_label),
    size = 2.5,
    angle = -90,
    hjust = 0,
    nudge_y = -0.05
  ) +
  scale_y_continuous(limits = c(-1, 1)) +
  theme_void() +
  coord_cartesian(clip = "off") +
  theme(
    plot.margin = margin(r = 10, l = 10, b = 10),
    legend.key = element_rect(fill = NA, color = NA),
    legend.text = element_text(size = 9),
    legend.title = element_text(size = 10, face = "bold"),
    legend.position = "none",
    plot.background = element_rect(fill = "white", color = NA)
  ) +
  labs(title = "DOJ Datasets")

legend_dummy <- data.frame(
    file_type = factor(names(c(
    audio = "#F35E5A",
    corrupt = "#A89005",
    email = "#17B12B",
    other = "#17B3B7",
    photo = "#5086FF",
    video = "#EF43DC"
)), levels = names(c(
    audio = "#F35E5A",
    corrupt = "#A89005",
    email = "#17B12B",
    other = "#17B3B7",
    photo = "#5086FF",
    video = "#EF43DC"
))),
    x = 1,
    y = 1
)

legend_plot <- ggplot(legend_dummy, aes(x = x, y = y, fill = file_type)) +
    geom_col() +
    scale_fill_manual(values = c(
    audio = "#F35E5A",
    corrupt = "#A89005",
    email = "#17B12B",
    other = "#17B3B7",
    photo = "#5086FF",
    video = "#EF43DC"
), drop = FALSE) +
    labs(fill = "File Type") +
    theme(
        legend.key = element_rect(fill = NA, color = NA),
        legend.text = element_text(size = 9),
        legend.title = element_text(size = 10, face = "bold")
    )

file_type_legend <- get_legend(legend_plot)
```

### Plots Combined

```{r}
#| echo: false
top2 <- files_sets + files_oversight + files_other +
  plot_layout(widths = c(length(unique(data_sets$file_origin)),
                         length(unique(data_oversight$file_origin)),
                         length(unique(data_other$file_origin)))) +
  theme(
    plot.margin = margin(b = 80)
  )

combined_2 <- (top2 / files_court) | file_type_legend

combined_2 <- combined_2 + 
  plot_layout(widths = c(4, 1), heights = c(3.2, 0.9)) &
  theme(plot.margin = margin(l = 10, r = 10, b = 52))

combined_2
```

## Number of files that have each page length

```{r}
length_table <- data |>
  filter(!is.na(file_length)) |>
  count(file_length, name = "Count") |>
  arrange(desc(Count)) |>
  rename(`Page Length` = file_length) |>
  mutate(Percent = round(Count / sum(Count) * 100, 2))

length_table
```

```{r}
#| echo: false
dp <- data |>
  filter(!is.na(file_length)) |>
  ggplot(aes(x = file_length)) +
  geom_histogram(binwidth = 50, fill = "black", color = "white") +
  scale_y_log10() + 
  scale_x_continuous(n.breaks = 6) +
  labs(x = "File Length",
       y = "Count (log)",
       title = "Overall Pattern of Page Lengths")
dp
```

## Total number of files that are emails

```{r}
data |>
  filter(file_type == "email") |>
  nrow()
```

## Total number of emails

```{r}
nrow(data_e)
```

## Which file numbers are missing

```{r}
DOJ <- data |>
  filter(!grepl("IMAGE", file_origin)) |>
  filter(!grepl("NATIVE", file_origin))

DOJ |>
  arrange(desc(file_origin))
```

```{r}
2847271 - 1396349
```

1,451,036 files are not released from the DOJ release, assuming numbers are sequential.

```{r}
Oversight <- data |>
  filter(grepl("IMAGE|NATIVE", file_origin))

Oversight |>
  arrange(desc(file_origin))
```

```{r}
33285 - 33376
```

```{r}
dup_rows <- Oversight |>
  mutate(file_id = str_extract(file_name, r"(DOJ-OGR-\d+)")) |>
  group_by(file_id) |>
  filter(n() > 1) |>
  ungroup() |>
  arrange(file_id, file_name)
```

166 files are duplicates, so 83 are duplicates.

## Missing Files By Dataset

```{r}
file_origin <- c("Data Set 1", 
                 "Data Set 2",
                 "Data Set 3",
                 "Data Set 4",
                 "Data Set 5",
                 "Data Set 6",
                 "Data Set 7",
                 "Data Set 8",
                 "Data Set 9",
                 "Data Set 10",
                 "Data Set 11",
                 "Data Set 12",
                 "CA Florida Holdings v. Aronberg",
                 "Doe 17 v. Indyke",
                 "Doe 1000 v. Indyke",
                 "Doe 3 v. Epstein",
                 "Doe 4 v. Epstein",
                 "Doe 5 v. Epstein",
                 "Doe 6 v. Epstein",
                 "Doe 8 v. Epstein",
                 "Doe 101 v. Epstein",
                 "Doe 102 v. Epstein",
                 "Doe 103 v. Epstein",
                 "Doe v. Epstein, 80069",
                 "Doe v. Epstein, 80119",
                 "Doe v. Epstein, 80804",
                 "Doe v. Epstein, 80469",
                 "Doe v. Indyke, 08673",
                 "Doe v. Indyke, 11869",
                 "Doe v. Indyke, 00484",
                 "Doe v. Indyke, 02365",
                 "Doe v. US",
                 "Epstein v. [Redacted]",
                 "Epstein v. Rothstein",
                 "US Virgin Islands v. JP Morgan Chase Bank",
                 "Doe 43 v. Epstein",
                 "Matter of the Estate of Jeffery Epstein",
                 "Maxwell v. Estate Jeffery Epstein",
                 "Maxwell v. US",
                 "Pension Fund v. Dimon",
                 "In re: Grand Jury 05-02 (WPB)",
                 "Florida v. Epstein, 009454",
                 "Florida v. Epstein, 009381",
                 "US v. Epstein, 2221",
                 "US v. Epstein, 00490",
                 "US v. Maxwell, 3061",
                 "US v. Maxwell, 0058",
                 "US v. Maxwell, 0770",
                 "US v. Maxwell, 1426",
                 "US v. Maxwell, 00330",
                 "US v. Maxwell, 00132",
                 "US v. Noel, 00830",
                 "[Redacted] v. Epstein, 81092",
                 "[Redacted] v. Epstein, 80447",
                 "[Redacted] v. Epstein, 81111",
                 "[Redacted] v. Indyke, 10474",
                 "[Redacted] v. Indyke, 10475",
                 "[Redacted] v. Indyke, 10476",
                 "[Redacted] v. Indyke, 10479",
                 "[Redacted] v. Indyke, 10488",
                 "[Redacted] v. Maxwell, 07433",
                 "[Redacted] v. Maxwell, 00025",
                 "[Redacted] v. Nine East 71st St",
                 "Customs and Border Protection (CBP)",
                 "Federal Bureau of Investigation (FBI)",
                 "Federal Bureau of Prisons (BOP)",
                 "Florida",
                 "First Phase of Declassified Epstein Files",
                 "BOP Video Footage",
                 "Maxwell Proffer",
                 "Memoranda and Correspondence")
file_start <- c(1, # dataset 1
                3159, # dataset 2
                3380, # dataset 3
                5705, # dataset 4
                8409, # dataset 5
                8529, # dataset 6
                9016, # dataset 7
                9676, # dataset 8
                39025, # dataset 9
                1262782, # dataset 10
                2209722, # dataset 11
                2730265, # dataset 12
                2732399, # court 1
                2737900, # court 2
                2737470, # court 3
                2739227, # court 4
                2740335, # court 5
                2741488, # court 6
                2742589, # court 7
                2743308, # court 8
                2738115, # court 9
                2738734, # court 10
                2739126, # court 11
                2743481, # court 12
                2743522, # court 13
                2749801, # court 14
                2750312, # court 15
                2750825, # court 16
                2751696, # court 17
                2751880, # court 18
                2752550, # court 19
                2752688, # court 20
                2759172, # court 21
                2759203, # court 22
                2805472, # court 23
                2819514, # court 24
                2821562, # court 25
                2821966, # court 26
                2822476, # court 27
                2822733, # court 28
                2819479, # court 29
                2823228, # court 30
                2823690, # court 31
                2824653, # court 32
                2824136, # court 33
                2843065, # court 34
                2843520, # court 35
                2824716, # court 36
                2844213, # court 37
                2829305, # court 38
                2843002, # court 39
                2845736, # court 40
                2820629, # court 41
                2732320, # court 42
                2820992, # court 43
                2777531, # court 44
                2777675, # court 45
                2819086, # court 46
                2731941, # court 47
                2737217, # court 48
                2778452, # court 49
                2758635, # court 50
                2845981, # court 51
                2847772, # foia 1
                2849279, # foia 2
                2850705, # foia 3
                2731891, # foia 4
                2846457, # first phase declassified
                2731862, # bop
                2731875, # foia 5
                2847271 # foia 6
)
file_end <- c(3158, # dataset 1
              3857, # dataset 2
              5586, # dataset 3
              8320, # dataset 4
              8527, # dataset 5
              8998, # dataset 6
              9664, # dataset 7
              39023, # dataset 8
              1262781, # dataset 9
              2212882, # dataset 10
              2730262, # dataset 11
              2858495, # dataset 12
              2737215, # court 1
              2738114, # court 2
              2737898, # court 3
              2740334, # court 4
              2741487, # court 5
              2742588, # court 6
              2743307, # court 7
              2743480, # court 8
              2738733, # court 9
              2739125, # court 10
              2739226, # court 11
              2743521, # court 12
              2749800, # court 13
              2750311, # court 14
              2750824, # court 15
              2751695, # court 16
              2751879, # court 17
              2752549, # court 18
              2752686, # court 19
              2758629, # court 20
              2759201, # court 21
              2777527, # court 22
              2819084, # court 23
              2820628, # court 24
              2821965, # court 25
              2822475, # court 26
              2822732, # court 27
              2823227, # court 28
              2819502, # court 29
              2823689, # court 30
              2824135, # court 31
              2824653, # court 32
              2824649, # court 33
              2843065, # court 34
              2844110, # court 35
              2825196, # court 36
              2844213, # court 37
              2842971, # court 38
              2843063, # court 39
              2845980, # court 40
              2820991, # court 41
              2732398, # court 42
              2821561, # court 43
              2777673, # court 44
              2778451, # court 45
              2819477, # court 46
              2732318, # court 47
              2737468, # court 48
              2805470, # court 49
              2759171, # court 50
              2846454, # court 51
              2849278, # foia 1
              2850658, # foia 2
              2853705, # foia 3
              2857520, # foia 4
              2846673, # first phase declassified
              2857523, # bop
              2847269, # foia 5
              2847765 # foia 6
              )
expected <- c(3158, # dataset 1
              699, # dataset 2
              1729, # dataset 3
              2734, # dataset 4
              208, # dataset 5
              470, # dataset 6
              666, # dataset 7
              29359, # dataset 8
              1223758, # dataset 9
              950101, # dataset 10
              517380, # dataset 11
              128235, # dataset 12
              NA_character_, # court 1
              NA_character_, # court 2
              NA_character_, # court 3
              NA_character_, # court 4
              NA_character_, # court 5
              NA_character_, # court 6
              NA_character_, # court 7
              NA_character_, # court 8
              NA_character_, # court 9
              NA_character_, # court 10
              NA_character_, # court 11
              NA_character_, # court 12
              NA_character_, # court 13
              NA_character_, # court 14
              NA_character_, # court 15
              NA_character_, # court 16
              NA_character_, # court 17
              NA_character_, # court 18
              NA_character_, # court 19
              NA_character_, # court 20
              NA_character_, # court 21
              NA_character_, # court 22
              NA_character_, # court 23
              NA_character_, # court 24
              NA_character_, # court 25
              NA_character_, # court 26
              NA_character_, # court 27
              NA_character_, # court 28
              NA_character_, # court 29
              NA_character_, # court 30
              NA_character_, # court 31
              NA_character_, # court 32
              NA_character_, # court 33
              NA_character_, # court 34
              NA_character_, # court 35
              NA_character_, # court 36
              NA_character_, # court 37
              NA_character_, # court 38
              NA_character_, # court 39
              NA_character_, # court 40
              NA_character_, # court 41
              NA_character_, # court 42
              NA_character_, # court 43
              NA_character_, # court 44
              NA_character_, # court 45
              NA_character_, # court 46
              NA_character_, # court 47
              NA_character_, # court 48
              NA_character_, # court 49
              NA_character_, # court 50
              NA_character_, # court 51
              NA_character_, # foia 1
              NA_character_, # foia 2
              NA_character_, # foia 3
              NA_character_, # foia 4
              NA_character_, # first phase declassified
              NA_character_, # bop
              NA_character_, # foia 5
              NA_character_ # foia 6
              )
actual <- c(3156, # dataset 1
          566, # dataset 2
          76, # dataset 3
          152, # dataset 4
          120, # dataset 5
          13, # dataset 6
          17, # dataset 7
          11014, # dataset 8
          533412, # dataset 9
          503946, # dataset 10
          331656, # dataset 11
          175, # dataset 12
          211, # court 1
          54, # court 2
          69, # court 3
          165, # court 4
          182, # court 5
          166, # court 6
          101, # court 7
          34, # court 8
          83, # court 9
          56, # court 10
          24, # court 11
          12, # court 12
          856, # court 13
          32, # court 14
          72, # court 15
          125, # court 16
          54, # court 17
          162, # court 18
          47, # court 19
          695, # court 20
          11, # court 21
          1412, # court 22
          1839, # court 23
          234, # court 24
          17, # court 25
          68, # court 26
          16, # court 27
          65, # court 28
          4, # court 29
          108, # court 30
          62, # court 31
          1, # court 32
          84, # court 33
          1, # court 34
          4, # court 35
          3, # court 36
          1, # court 37
          1019, # court 38
          5, # court 39
          66, # court 40
          26, # court 41
          17, # court 42
          72, # court 43
          41, # court 44
          147, # court 45
          62, # court 46
          53, # court 47
          59, # court 48
          2965, # court 49
          77, # court 50
          91, # court 51
          8, # foia 1
          22, # foia 2
          4, # foia 3
          77, # foia 4
          4, # first phase declassified
          16, # bop
          21, # foia 5
          6 # foia 6
          )
not_released <- c(2, # dataset 1
                  133, # dataset 2
                  649, # dataset 3
                  2582, # dataset 4
                  88, # dataset 5
                  457, # dataset 6
                  649, # dataset 7
                  18345, # dataset 8
                  690346, # dataset 9
                  446155, # dataset 10
                  185724, # dataset 11
                  128060, # dataset 12
                  NA_character_, # court 1
                  NA_character_, # court 2
                  NA_character_, # court 3
                  NA_character_, # court 4
                  NA_character_, # court 5
                  NA_character_, # court 6
                  NA_character_, # court 7
                  NA_character_, # court 8
                  NA_character_, # court 9
                  NA_character_, # court 10
                  NA_character_, # court 11
                  NA_character_, # court 12
                  NA_character_, # court 13
                  NA_character_, # court 14
                  NA_character_, # court 15
                  NA_character_, # court 16
                  NA_character_, # court 17
                  NA_character_, # court 18
                  NA_character_, # court 19
                  NA_character_, # court 20
                  NA_character_, # court 21
                  NA_character_, # court 22
                  NA_character_, # court 23
                  NA_character_, # court 24
                  NA_character_, # court 25
                  NA_character_, # court 26
                  NA_character_, # court 27
                  NA_character_, # court 28
                  NA_character_, # court 29
                  NA_character_, # court 30
                  NA_character_, # court 31
                  NA_character_, # court 32
                  NA_character_, # court 33
                  NA_character_, # court 34
                  NA_character_, # court 35
                  NA_character_, # court 36
                  NA_character_, # court 37
                  NA_character_, # court 38
                  NA_character_, # court 39
                  NA_character_, # court 40
                  NA_character_, # court 41
                  NA_character_, # court 42
                  NA_character_, # court 43
                  NA_character_, # court 44
                  NA_character_, # court 45
                  NA_character_, # court 46
                  NA_character_, # court 47
                  NA_character_, # court 48
                  NA_character_, # court 49
                  NA_character_, # court 50
                  NA_character_, # court 51
                  NA_character_, # foia 1
                  NA_character_, # foia 2
                  NA_character_, # foia 3
                  NA_character_, # foia 4
                  NA_character_, # first phase declassified
                  NA_character_, # bop
                  NA_character_, # foia 5
                  NA_character_ # foia 6
                  )
counts <- data.frame(file_origin, file_start, file_end, expected, actual, not_released)
```

```{r}
counts |>
  mutate(file_origin = fct_reorder(file_origin, file_start, .desc = TRUE)) |>
  filter(file_origin != "Data Set 1") |>
  filter(file_origin != "Data Set 2") |>
  filter(file_origin != "Data Set 3") |>
  filter(file_origin != "Data Set 4") |>
  filter(file_origin != "Data Set 5") |>
  filter(file_origin != "Data Set 6") |>
  filter(file_origin != "Data Set 7") |>
  filter(file_origin != "Data Set 8") |>
  filter(file_origin != "Data Set 9") |>
  filter(file_origin != "Data Set 10") |>
  filter(file_origin != "Data Set 11") |>
  ggplot(aes(y = file_origin)) +
  geom_segment(
    aes(x = file_start, xend = file_end, yend = file_origin),
    lineend = "round"
  ) +
  scale_x_continuous(labels = scales::comma) +
  labs(
    x = "File ID",
    y = NULL,
    title = "File ID ranges by dataset origin"
  ) +
  theme_minimal(base_size = 9) +
  theme(
    panel.grid.minor = element_blank(),
    plot.title = element_text(size = 12, face = "bold")
  )
```

```{r}
one_six <- counts |>
  mutate(file_origin = fct_reorder(file_origin, file_start, .desc = TRUE)) |>
  filter(grepl("Data Set", file_origin)) |>
  filter(file_origin != "Data Set 12") |>
  filter(file_origin != "Data Set 11") |>
  filter(file_origin != "Data Set 10") |>
  filter(file_origin != "Data Set 9") |>
  filter(file_origin != "Data Set 8") |>
  filter(file_origin != "Data Set 7") |>
  ggplot(aes(y = file_origin)) +
  geom_segment(
    aes(x = file_start, xend = file_end, yend = file_origin),
    lineend = "round"
  ) +
  scale_x_continuous(labels = scales::comma) +
  labs(
    x = "File ID",
    y = NULL,
    title = "File ID ranges by dataset origin"
  ) +
  theme_minimal(base_size = 9) +
  theme(
    panel.grid.minor = element_blank(),
    plot.title = element_text(size = 12, face = "bold")
  )
```

```{r}
seven_twelve <- counts |>
  mutate(file_origin = fct_reorder(file_origin, file_start, .desc = TRUE)) |>
  filter(grepl("Data Set", file_origin)) |>
  filter(file_origin != "Data Set 1") |>
  filter(file_origin != "Data Set 2") |>
  filter(file_origin != "Data Set 3") |>
  filter(file_origin != "Data Set 4") |>
  filter(file_origin != "Data Set 5") |>
  filter(file_origin != "Data Set 6") |>
  ggplot(aes(y = file_origin)) +
  geom_segment(
    aes(x = file_start, xend = file_end, yend = file_origin),
    lineend = "round"
  ) +
  scale_x_continuous(labels = scales::comma) +
  labs(
    x = "File ID",
    y = NULL,
    title = "File ID ranges by dataset origin"
  ) +
  theme_minimal(base_size = 9) +
  theme(
    panel.grid.minor = element_blank(),
    plot.title = element_text(size = 12, face = "bold")
  )
```

```{r}
ggsave(
    filename = file.path("/Volumes/Thesis/plots/1_files_by_type.png"),
    plot = files_by_type,
    width = 8, height = 5, dpi = 300
)

ggsave(
    filename = file.path("/Volumes/Thesis/plots/2_totals_court.png"),
    plot = totals_court,
    width = 8, height = 5, dpi = 300
)

ggsave(
    filename = file.path("/Volumes/Thesis/plots/3_totals_other.png"),
    plot = totals_other,
    width = 8, height = 5, dpi = 300
)

ggsave(
    filename = file.path("/Volumes/Thesis/plots/4_totals_oversight.png"),
    plot = totals_oversight,
    width = 8, height = 5, dpi = 300
)

ggsave(
    filename = file.path("/Volumes/Thesis/plots/5_totals_set.png"),
    plot = totals_set,
    width = 8, height = 5, dpi = 300
)

ggsave(
    filename = file.path("/Volumes/Thesis/plots/6_files_court.png"),
    plot = files_court,
    width = 8, height = 5, dpi = 300
)

ggsave(
    filename = file.path("/Volumes/Thesis/plots/7_files_other.png"),
    plot = files_other,
    width = 8, height = 5, dpi = 300
)

ggsave(
    filename = file.path("/Volumes/Thesis/plots/8_files_oversight.png"),
    plot = files_oversight,
    width = 8, height = 5, dpi = 300
)

ggsave(
    filename = file.path("/Volumes/Thesis/plots/9_files_sets.png"),
    plot = files_sets,
    width = 8, height = 5, dpi = 300
)

ggsave(
    filename = file.path("/Volumes/Thesis/plots/10_one_six.png"),
    plot = one_six,
    width = 8, height = 5, dpi = 300
)

ggsave(
    filename = file.path("/Volumes/Thesis/plots/10_seven_twelve.png"),
    plot = seven_twelve,
    width = 8, height = 5, dpi = 300
)

ggsave(
    filename = file.path("/Volumes/Thesis/plots/11_file_type_legend.png"),
    plot = file_type_legend,
    width = 8, height = 5, dpi = 300
)

ggsave(
    filename = file.path("/Volumes/Thesis/plots/12_combined.png"),
    plot = combined,
    width = 8, height = 5, dpi = 300
)
```

```{r}
ggsave(
    filename = file.path("/Volumes/Thesis/plots/13_combined_2.png"),
    plot = combined_2,
    width = 8, height = 6.2, dpi = 300
)
```

```{r}
extraction <- read_csv("/Volumes/Thesis/Epstein_Files/output/extraction_combined.csv")
```

```{r}
extraction |>
  filter(grepl("No Images Produced", text, ignore.case = TRUE))
```

```{r}
data <- data |>
  mutate(extension = sub(".*\\.", "", file_name))
```

```{r}
data <- data |>
  filter(extension != "TheJusticeDept") |>
  filter(extension != "dl?inline") |>
  filter(extension != "guidance") |>
  filter(extension != "information-victims-large-cases")
```

```{r}
ext <- ggplot(data) +
  aes(extension) +
  geom_bar(fill = "grey80", color = "grey78") +
  geom_text(aes(label = after_stat(count)), 
            stat = "count",
            size = 6,
            size.unit = "pt",
            vjust = -0.3) +
  theme_void() +
  theme(axis.title.y = element_blank(), # remove label
        axis.text.y = element_blank(), # remove number
        axis.ticks.y = element_blank(), # remove ticks
        axis.line.y = element_blank(), # remove line (blank here)
        axis.title.x = element_blank(),
        axis.text.x = element_text(
          size = 6,
          angle = -90,
          hjust = 0,
          vjust = 0.5),
        plot.margin = margin(r = 10, l = 10, b = 10),
        plot.background = element_rect(fill = "white", color = NA)
  ) + 
  labs(title = "Total numbers by file extension")

ext
```

```{r}
ggsave(
    filename = file.path("/Volumes/Thesis/plots/14_ext.png"),
    plot = ext,
    width = 8, height = 5, dpi = 300
)
```

```{r}
ggsave(
    filename = file.path("/Volumes/Thesis/plots/15_page_length.png"),
    plot = dp,
    width = 8, height = 5, dpi = 300
)
```

```{r}
data_EFTA <- data |>
  filter(grepl("EFTA", file_name))
```

```{r}
#| eval: false
files_by_type_EFTA <- ggplot(data = data_EFTA,
       aes(
         x = file_type,
         fill = file_type
       )) +
  scale_fill_manual(values = c(
    audio = "#F35E5A",
    corrupt = "#A89005",
    email = "#17B12B",
    other = "#17B3B7",
    photo = "#5086FF",
    video = "#EF43DC"),
    drop = FALSE
  ) +
  geom_bar() +
  geom_text(aes(label = after_stat(count)), 
            stat = "count",
            size = 6,
            size.unit = "pt",
            vjust = -0.3) +
  scale_y_sqrt() +
  theme_void() +
  theme(
    plot.margin = margin(r = 10, l = 10, b = 10),
    axis.title.y = element_blank(), # remove label
    axis.text.y = element_blank(), # remove number
    axis.ticks.y = element_blank(), # remove ticks
    axis.line.y = element_blank(), # remove line (blank here)
    axis.text.x = element_text(), # restore x tick labels
    axis.title.x = element_blank(), # restore x axis title
    legend.position = "none",
    plot.background = element_rect(fill = "white", color = NA)
        ) + 
  labs(title = "Total number of files by type - EFTA release")
files_by_type_EFTA
```

```{r}
ggsave(
    filename = file.path("/Volumes/Thesis/plots/16_files_by_type_EFTA.png"),
    plot = files_by_type_EFTA,
    width = 8, height = 5, dpi = 300
)
```

```{r}
nrow(data_EFTA)
```

```{r}
sum(data_EFTA$file_length, na.rm = TRUE)
```
